Arc Blanc: a real time ocean simulation framework

### 2024-11-12 paper.tex
Use correct quotation mark

\subsubsection{Ocean free surface simulation}
\label{subsubsec:oceanFreeSurfaceSim}
J. Tessendorf (2004) \cite{tessendorfSimulatingOceanWater1999} presented what could be considered a seminal work in real-time ocean simulation. His work relies on the Fast Fourier Transform (FFT) and statistical wave spectra to accurately find the analytical solutions to an approximation of the Navier-Stokes equation on a 2D height field. This method is commonly known as the "Tessendorf method".

The realism of this method was significantly improved by Horvath (2015) \cite{horvathEmpiricalDirectionalWave2015}, who proposed an empirically based directional spectrum.
In addition, he proposed to add a parameter called "swell", which allows the transition from empirical directional propagation to parallel waves.

@@

In \framework, the directional spectrum relies on the work of Horvath (2015) \cite{horvathEmpiricalDirectionalWave2015}, that mixes together the Donelan-Banner spectrum to control the direction of the waves and a "swell parameter".
Let us recall that, if the wind direction is given by $\theta_0$, the wind direction bias $\theta$ can be defined as follows:
\begin{equation}
	\theta = atan2(k_z, k_x) - \theta_0
\end{equation}
Moreover, the Donelan-Banner $D_{DB}$ spectrum is given as follows:
\begin{equation}
	D_{DB}\left(\omega,\theta\right)=\frac{1}{2}Q_{DB}\left(\omega\right)\beta_s\left(\operatorname{sech}\left(\beta_s\theta\right)\right)^2.
	\label{equa:ddb}
\end{equation}

@@

First, it should be noticed that the expressions of the ocean surface's height (Equation~\ref{equa:heightWater}), the displacements (Equation~\ref{equa:hori-displacement}) and their five derivatives, and the velocity (Equation~\ref{equa:velocity}) have "a form of an inverse discrete Fourier transform".
More precisely, the \textbf{frequency space} coefficients appearing before the term $\exp(i\mathbf{k}\cdot\mathbf x)$ are stored in a square matrix of size $N\times N$, for each expression.
Then, the full sum is computed through an \textbf{inverse fast Fourier transform} (IFFT) applied on this coefficients' matrix.
In \framework, this trick allows computing these eight expressions without any significant impact on performance, even for huge domains.

@@

This distribution is designed based on the following considerations.
First, while the velocity decays exponentially, it relies on a logarithmic similar to $y_i\mapsto \ln(|y_i|+1)$.
Since this function transforms the negative $y_i$ into a positive one, the result is multiplied by the sign of $y_i$.
Also, this function decreases slowly (actually with $\ln(250+1)=5.5$), hence the logarithmic distribution uses the square of $|y_1|$.
Lastly, the parameter $\alpha$ controls the "squeezing" in the center, while the parameter $\beta$ controls the deepest value of $d$.
Notice that $\beta$ is chosen as the solution of $d(y_{min})=\frac{y_{min}}{2}$ but not at $y_{min}$: it is the solution giving the best accuracy after multiple tries.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Remove quadratic term}
The quadratic term in the Bernoulli equation \ref{equa:bernoulli} makes solving the equation too complex.
Therefore, the velocity is assumed to be sufficiently small to neglect the quadratic term relative to the others.
It leads to the "final" Bernoulli equation expressed as follows:
\begin{equation}
	\frac{\partial \phi}{\partial t} = -gh(\mathbf x,t) \label{equa:bernoulliS}
\end{equation}

>>>>

\subsubsection{Ocean free surface simulation}
\label{subsubsec:oceanFreeSurfaceSim}
J. Tessendorf (2004) \cite{tessendorfSimulatingOceanWater1999} presented what could be considered a seminal work in real-time ocean simulation. His work relies on the Fast Fourier Transform (FFT) and statistical wave spectra to accurately find the analytical solutions to an approximation of the Navier-Stokes equation on a 2D height field. This method is commonly known as the “Tessendorf method”.

The realism of this method was significantly improved by Horvath (2015) \cite{horvathEmpiricalDirectionalWave2015}, who proposed an empirically based directional spectrum.
In addition, he proposed to add a parameter called “swell”, which allows the transition from empirical directional propagation to parallel waves.

@@

In \framework, the directional spectrum relies on the work of Horvath (2015) \cite{horvathEmpiricalDirectionalWave2015}, that mixes together the Donelan-Banner spectrum to control the direction of the waves and a “swell parameter”.
Let us recall that, if the wind direction is given by $\theta_0$, the wind direction bias $\theta$ can be defined as follows:
\begin{equation}
	\theta = atan2(k_z, k_x) - \theta_0
\end{equation}
Moreover, the Donelan-Banner $D_{DB}$ spectrum is given as follows:
\begin{equation}
	D_{DB}\left(\omega,\theta\right)=\frac{1}{2}Q_{DB}\left(\omega\right)\beta_s\left(\operatorname{sech}\left(\beta_s\theta\right)\right)^2.
	\label{equa:ddb}
\end{equation}

@@

First, it should be noticed that the expressions of the ocean surface's height (Equation~\ref{equa:heightWater}), the displacements (Equation~\ref{equa:hori-displacement}) and their five derivatives, and the velocity (Equation~\ref{equa:velocity}) have “a form of an inverse discrete Fourier transform”.
More precisely, the \textbf{frequency space} coefficients appearing before the term $\exp(i\mathbf{k}\cdot\mathbf x)$ are stored in a square matrix of size $N\times N$, for each expression.
Then, the full sum is computed through an \textbf{inverse fast Fourier transform} (IFFT) applied on this coefficients' matrix.
In \framework, this trick allows computing these eight expressions without any significant impact on performance, even for huge domains.

@@

This distribution is designed based on the following considerations.
First, while the velocity decays exponentially, it relies on a logarithmic similar to $y_i\mapsto \ln(|y_i|+1)$.
Since this function transforms the negative $y_i$ into a positive one, the result is multiplied by the sign of $y_i$.
Also, this function decreases slowly (actually with $\ln(250+1)=5.5$), hence the logarithmic distribution uses the square of $|y_1|$.
Lastly, the parameter $\alpha$ controls the “squeezing” in the center, while the parameter $\beta$ controls the deepest value of $d$.
Notice that $\beta$ is chosen as the solution of $d(y_{min})=\frac{y_{min}}{2}$ but not at $y_{min}$: it is the solution giving the best accuracy after multiple tries.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Remove quadratic term}
The quadratic term in the Bernoulli equation \ref{equa:bernoulli} makes solving the equation too complex.
Therefore, the velocity is assumed to be sufficiently small to neglect the quadratic term relative to the others.
It leads to the “final” Bernoulli equation expressed as follows:
\begin{equation}
	\frac{\partial \phi}{\partial t} = -gh(\mathbf x,t) \label{equa:bernoulliS}
\end{equation}
